Tables

### 2023-11-10 output/paper/tables.qmd
Kept working on processing results for paper.
Added target to produce figures for overlap exposures. Fixed tables for obs numbers afrer weighting and trimming.

>>>>

```{r}
targets::tar_load(
  dplyr::matches("balance_(\\d)$"),
  store = store
)
```

```{r balance-1}
#| label: tbl-balance-1
#| tbl-cap: Effective number of observations

balance_1 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```

```{r balance-2}
#| label: tbl-balance-2
#| tbl-cap: Effective number of observations

balance_2 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```

```{r balance-3}
#| label: tbl-balance-3
#| tbl-cap: Effective number of observations

balance_3 |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```
